---
title: "AI Part 1 Analysis"
output: word_document
date: "2023-08-18"
---

#Introduction 
In this analysis we have explored the Twitter dataset related to popular Netflix show Squid Game. The analysis presents the frequency of the tweets, top tweeting locations including the top 10, and the most retweeted tweets including the top 20. 

```{r}
#Load required libraries 
library(dplyr)
library(ggplot2)
```
#Data imported
```{r}
 rm(list=ls())
 squidgame <- read.csv("C:/Users/sumitra/Desktop/squidgame.csv", comment.char="#")
 View(squidgame)

```
#The data loaded and cleaned 
```{r}
library(dplyr)
library(ggplot2)
 squidgame$text[squidgame$text == ""] <- NA
 squidgame$source[squidgame$source == ""] <- NA
 squidgame$user_description[squidgame$user_description == ""] <- NA
 squidgame$user_location[squidgame$user_location == ""] <- NA
 cleaned_tweets<-na.omit(squidgame)
 View(cleaned_tweets)
```
#Reviewing the dataset and visualizing the frequency of the squid game tweets

```{r}
# Convert timestamps
cleaned_tweets$date <- as.POSIXct(strptime(cleaned_tweets$date, format = "%Y-%m-%d %H:%M:%S"), tz = "UTC")

# Create a time-based histogram of tweet frequencies
ggplot(data = cleaned_tweets, aes(x = date)) +
    geom_histogram(binwidth = 60*60, fill = "blue", color = "black") +
    labs(title = "Squid Game Tweet Frequency Over Time", x = "Time", y = "Number of Tweets") +
    scale_x_datetime(date_labels = "%Y-%m-%d %H:%M", date_breaks = "1 hour")
library(stringr)
# Extract hashtags from tweets
hashtags <- unlist(str_extract_all(cleaned_tweets$text, "#\\w+"))

```

#Identifying top tweeting locations including top 10
```{r}
library(dplyr)

# Group by user_location and count the number of tweets in each location
top_locations <- cleaned_tweets %>%
    group_by(user_location) %>%
    summarise(tweet_count = n()) %>%
    arrange(desc(tweet_count))

# View the top locations data
View(top_locations)
 # Display the first 10 top tweeting locations
 head(top_locations, 10)
# A tibble: 10 × 2
#The data shows that the top 10 tweeting locations are India, Los Angeles;CA, United States, Dubai, London, United Kingdom, Mumbai, Canada. 

```
#Most retweeted tweets including top 20 
```{r}
 # Load necessary libraries
# Load necessary libraries
library(dplyr)

# Arrange tweets in descending order of retweet count
top_retweeted_tweets <- cleaned_tweets %>%
    arrange(desc(is_retweet))
 # Display the top 20 most retweeted tweets
 head(top_retweeted_tweets, 20)
#The dataset below shows the top 20 users along with their user location, descprition and source, whose tweets have been most retweeted. 
```

```{r}
# Arrange the dataset by is_retweet in descending order and select the top 20
top_retweeted <- cleaned_tweets %>%
    arrange(desc(is_retweet)) %>%
    head(20)
View(top_retweeted)
```

